The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2014-02-03 document/ms.tex
some words

\paragraph{Preconditioning}
Then, we mask the data within 1.5 transit durations and fit the maximum
likelihood line to the remaining data points.
Finally, we divide the full window by this model to generate a ``de-trended''
light curve.
This procedure has been applied successfully in the literature (Carter ETC
CITE) and it should be less destructive to transit signals than alternative
techniques like median filtering and ``robust'' regression.

@@

\paragraph{Generative model}
For this project, we assume a quadratic limb darkened light curve model
following Mandel \& Agol (CITE) and integrate over exposure time (Kipping
CITE, Appendix XXXX).
Since we don't want to be dependent on specific stellar parameters and since
we would like to make it easy to apply any new stellar catalogs, we don't use
physical orbits.
Instead, we parameterize the orbit using only ``observable'' parameters.
In particular, we use, for the star, the mean stellar flux \fstar, and the
parameters \qone\ and \qtwo\ of a quadratic limb darkening profile
(parameterized following Kipping CITE).
For each companion, we parameterize the orbit using period \period, epoch
\epoch, transit duration \duration, radius ratio \ror, and impact parameter
\impact.
\Tab{parameters} specifies the parameters used in this \paper\ and the
interim priors used.

>>>>

\paragraph{Preconditioning}
These light curves still include some systematic noise and stellar
variability.
To remove this signal, we mask the data within 1.5 transit durations and find
the maximum likelihood cubic polynomial trend conditioned on the remaining
measurements.
In order to avoid over-fitting, we apply a weak L2 regularization to the
likelihood:
\begin{eqnarray}
\ell(\bvec{c}) &=& -\frac{1}{2}\sum_{n=1}^N \frac{[f_n - m(t_n; \bvec{c})]^2}
                                                 {\sigma_n^2}
                   -\frac{\lambda}{2} \left | \bvec{c} \right |^2
\end{eqnarray}
where
\begin{eqnarray}
m(t_n;\bvec{c}) &=& c_0 + c_1\,t_n + c_2\,t_n^2 + c_3\,t_n^3 \quad.
\end{eqnarray}
In practice, after some extremely scientific experiments, we chose to use
$\lambda = 1$ for every light curve.

Finally, we divide the full window of observations by the predicted trend
$m(t_n;\bvec{c})$ to produce a ``de-trended'' light curve.
A similar procedure has been applied successfully in the literature (Carter ETC
CITE) and it should be less destructive to transit signals than alternative
techniques like median filtering and ``robust'' regression.

@@

\paragraph{Generative model}
For this project, we assume a quadratic limb darkened light curve model
following Mandel \& Agol (CITE) and integrate over exposure time using an
adaptive algorithm described in Appendix (XXXX).
Since we don't want to be dependent on specific stellar parameters and since
we would like to make it easy to apply any new constraints on the stellar
parameters, we don't require physical orbits.
Instead, we parameterize the orbit using only ``observable'' parameters.
This is a somewhat controversial choice as we will discuss in Section (YYYY).

In particular, we use, for the star, the mean stellar flux \fstar, and the
parameters \qone\ and \qtwo\ of a quadratic limb darkening profile.
The limb darkening law is parameterized following Kipping (CITE) and the
coefficients are related to the standard parameterization
\begin{eqnarray}
I(\mu) &=& 1 - u_1\,(1-\mu) - u_2\,(1-\mu)^2 \\
\mu &=& \sqrt{1-r^2}
\end{eqnarray}
by
\begin{eqnarray}
q_1 &=& (u_1 + u_2)^2 \\
q_2 &=& \frac{u_1}{2\,(u_1+u_2)} \quad.
\end{eqnarray}
For each companion, we parameterize the orbit using period \period, epoch
\epoch, transit duration \duration, radius ratio \ror, and impact parameter
\impact.
\Tab{parameters} specifies the parameters used in this \paper\ and the
interim priors used.
